---
title: "Attempting to data clean and merge Actilife and GPS data files"
output: 
  html_notebook:
        toc: yes
        toc_float: true

---

# Loading packages

Our intention is to use packages from the tidyverse and other *tidy* packages to provide a constistant framework.                                                                                                                                                                                                                                                  

```{r}
library(DT)
library(plotly)
library(tidyverse) # data manipulation and visualization - loads several packages
library(readr) # reading data files
library(lubridate) # working with dates
library(tibbletime)
library(tidyquant)
library(sf)
library(tmap)
library(crosstalk)
library(leaflet)


```

# Data munging

## Load and clean ActiLife Data

Read the file and create new column which encodes data-time as a single variable.

Using `tibbletime` commands, we will make this dataframe "time aware".

We are basing these manipulations off the tutorial 
http://www.business-science.io/code-tools/2017/10/26/demo_week_tibbletime.html .


```{r warning=FALSE,message=FALSE}
df=read_csv("Autumn ActiLife Data.csv",skip=10)
df <- df %>% mutate(Date=mdy(Date)) %>% mutate(date_time=ymd_hms(paste(Date,Time))) %>%
  janitor::clean_names() %>%
  as_tbl_time(index = date_time)


str(df)
```

## Load and clean GPS data

First we load as a data frame and create a date-time variable.



```{r}
df2 <- read_csv("Autumn 7-1-18.csv") %>% mutate(Date=mdy(Date)) %>% rename(Time='Time (local)') %>%
  mutate(date_time=ymd_hms(paste(Date,Time))) %>% janitor::clean_names()


```

We convert do a tibbletime object and change the periodicity to 1 minute intervals.  

We chose to average all data from time xx:xx:00-xx:xx:59, and then round down to the nearest minute

```{r}

df3_tt=df2 %>%
    as_tbl_time(index = date_time) %>% 
  as_period("minutes",side="start" ) %>% mutate(date_time=floor_index(date_time,unit="minutes"))



```

## Merge the two data frames

We will merge all of the data, recognizing that not all times exist in both data sets, but we also create `dfg`, which restricts to those points with gps data

```{r}
dffull=full_join(df,df3_tt,by="date_time") 

dfg=right_join(df,df3_tt,by="date_time") 

```

# Some visualizations using ggplot2

```{r eval=FALSE}
dfg %>% ggplot( aes(x=date_time, y= longitude,col=speed_mi_hr)) +geom_point(aes())

```

```{r eval=FALSE}
dfg %>% ggplot( aes(x=date_time, y= latitude,col=speed_mi_hr)) +geom_point(aes())

```

```{r eval=FALSE}
dfg %>% ggplot( aes(x=longitude, y= latitude,col=steps)) +geom_point(aes())

```

# Creating sf object and looking at Maps

We create a *sf* simple features object in an `xy` coordinate system and plot using ggplot.

```{r}
dfg1=st_as_sf(dfg, coords=c("longitude" ,"latitude"))

#dfg1 %>% ggplot(aes(col=steps)) + geom_sf() +theme_minimal()+ scale_colour_viridis_c()

```

We also plot this data on a `tmap` plot:

```{r}
tmap_mode("view")
#tmap_mode("plot")
tm_shape(dfg1) + 
  tm_dots("inclinometer_standing")+ 
  tm_view(alpha = 1,basemaps.alpha = 1)+
  tm_basemap(c(Canvas = "Esri.WorldGrayCanvas", Imagery = "Esri.WorldImagery",OpenStreet="OpenStreetMap"))

```


# Can we do a multiview plot with crosstalk?


```{r}

sd=SharedData$new(dfg1)



p1=tm_shape(sd$data()) + 
  tm_dots("speed_mi_hr")+ 
  tm_view(alpha = 1,basemaps.alpha = 1)+
  tm_basemap(c(Canvas = "Esri.WorldGrayCanvas", Imagery = "Esri.WorldImagery"))

lf <- tmap_leaflet(p1)

p2=datatable(sd)

p3=sd %>% ggplot(aes(x=date_time,y=steps))+geom_point() 



ggplotly(p3) %>%   highlight("plotly_selected", dynamic = TRUE)


p1=leaflet(sd) %>% addProviderTiles("OpenStreetMap") %>% addCircles()

p1

# bscols(p1,datatable(sd))

bscols(p1,ggplotly(p3) %>%   highlight("plotly_selected", dynamic = TRUE))

#bscols( lf, ggplotly(p3) %>% highlight(color="red"))

#bscols( lf, datatable(sd))

#bscols( ggplotly(p3), datatable(sd))

```











